### 2020-09-01 paper_review/response_20200826.txt

******************************************
REFEREE COMMENT
----------
Sec. 2.2
It seems another line of evidence against Star B (rho=5.4 arcsec)
as the host is the difference imaging centroid test mentioned in
Section 2.1, which they state localizes the transit to within 2
arcseconds of the target.

RESPONSE
----------
> Correct -- we have modified the wording in Sec 2.4 to clarify
> this point.

******************************************
REFEREE COMMENT
----------
Given that TOI 837 and Star A have a large contrast but similar
distances, I would expect the two stars to have a large
difference in their expected densities. Can the mean stellar
density from the transit fit be used to further argue that the
planet orbits TOI 837?

RESPONSE
----------
> Our thanks for pointing this out. We have added a paragraph at
> the end of Section 2.4.1 to this effect.

@@

******************************************
REFEREE COMMENT
----------
Sec. 4.1.2
The statement that TOI 837 lies along the empirical cluster
isochrone and this limits the presence of a companion to be <50%
the brightness seems to be misstated. I believe the authors mean
that TOI 837 appears to lie below the equal-brightness binary
sequence (which sits 0.75 mag above the single star sequence).
This limits a hypothetical companion to be less than the
brightness of the target star (or less than 50% the total system
brightness).

RESPONSE
----------
> Thank you for raising this point. Our original writing was in
> error, because we meant something slightly stronger. If TOI 837
> were an equal-brightness binary system, it would be 0.75
> magnitudes above the single star sequence. However TOI 837 is
> not only not on the equal-brightness binary sequence -- it is
> not at all elevated with respect to the single-star sequence. A
> binary companion with say half the brightness of the primary
> would make the system 0.44 mags brighter than the single star
> sequence. Based on the intrinsic scatter in the HR diagram,
> this is also ruled out.  We (imprecisely) meant this second
> point, and have modified the text accordingly.

******************************************
REFEREE COMMENT
----------
Sec. 4.2.4
It is not immediately clear that the mass-temperature-age
combination of ~1.2 Msun, 5960 K, and 30-45 Myr is incorrect. The
mass-temperature relation for stars in this mass range is not the
same on the pre-main sequence as it is on the main sequence.

RESPONSE
----------
> Looking at the MIST isochrones, it seems that a
> solar-metallicity, 1.1Msun star reaches the ZAMS around
> log(age) of 7.5, or ~32 Myr. So, TOI 837 seems likely to be
> roughly at the ZAMS, rather than particularly early in its
> pre-main sequence contraction.
>
> Regardless, we have modified the wording here to reflect that
> our preference for the stellar parameters from "Method 2" is
> linked to our ability to more easily quantify its uncertainties
> (statistical and systematic -- see below).

@@

******************************************
REFEREE COMMENT
----------
Sec. 4.2.4
The authors are encouraged to explore the effect of adopting a
different set of evolutionary models. The Dartmouth models of
Feiden (2016), which include a magnetic field prescription, have
been shown to more accurately reproduce the parameters of
pre-main sequence stars. In the mass range of TOI 837 the effects
may not be dramatic, but are likely to be significant compared to
the quoted uncertainty on e.g. the stellar mass. I would expect
that a 10% uncertainty on the stellar mass would be more
realistic (in the sense that it would accommodate systematic
uncertainties) than the currently quoted 1% uncertainty.

RESPONSE
----------
> Thank you for this suggestion, which we agree is important. We
> amended Section 4.2.4 to explore the use of the PARSEC models
> in addition to the MIST models. (We checked the Feiden 2016
> Dartmouth models, but no synthetic Gaia-band photometry was
> available, which complicates the comparison between between the
> Gaia photometry and the models.) The differences between MIST
> and PARSEC are now described in the text, and are used to
> estimate systematic uncertainties on the stellar parameters.
> These uncertainties are now reported in Table 4, and they are
> also propagated through the transit fits (Table 5; Figure 1;
> Figure 4; Figure 10). 
>
> Compared to the initially submitted TESS-only transit fit, the
> wider priors on R* and logg* exacerbated the impact parameter
> vs Rp/R* degeneracy.  With the wider stellar density prior,
> impact parameters much greater than 1 became statistically
> allowed (though not favored), if the planet-to-star radius
> ratio were to be very large. Our ability to break the
> degeneracy was broken! Given only the TESS data + the
> isochronal stellar parameter priors with systematic
> uncertainties included, only a one-sided limit on the planet
> radius can be derived.
>
> One way to "fix" this issue would have been to impose a prior
> constraint that Rp<3Rjup, based on our mass upper limit of
> ~2Mjup and the fact that all known planetary and stellar
> objects follow mass-radius relations that would require the
> planet to be smaller than 3Rjup. However, this approach would
> be somewhat atypical, and even when doing it, we found with our
> updated stellar uncertainties that the TESS-only model (with Rp
> limit prior) gave:
>
>   TESS-only, Rp<3Rjup assumed, systematic star uncertainties:
>     r_planet [Rjup]: 0.836 +0.208 -0.121
>     b: 0.957 +0.027 -0.017
> 
> where we quote median, 86th, and 14th percentiles. Conversely,
> the fit to the combined TESS+ground data yielded a planet
> radius more precise by a factor of ~2x: 
>
>   TESS+ground, broad Rp/R* prior, systematic star uncertainties:
>     r_planet [Rjup]: 0.768 +0.091 -0.072
>     b: 0.936 +0.013 -0.010
>
> Given the increase from 5 to 12 transits, this is presumably
> because the transit depth is measured more precisely. (Both
> sets of chains are fully converged, with Rhat-1 < 1e-4).
> Despite our initial reservations about using the ground-based
> data for the planet parameters, the combined data do yield a more
> precise fit, and also seem to do a better job at breaking the Rp/R*
> vs b degeneracy. These two points persuaded us to adopt it as our
> preferred solution.  Nonetheless, this decision is one of
> preference, and not modelling necessity. We have amended Section 4.3
> at some length to present the points made in this response, and to
> emphasize the key results from both approaches.  Consequent changes
> include:
>
> * Bottom panel of Figure 1 now shows the TESS+ground data
>   phase-folded, instead of TESS-only. Caption was updated
>   accordingly.
>
> * Figure 10 is now the posterior from TESS+ground, instead of
>   TESS-only.
>
> * Figure 11 was updated for the new planet radius.  
>
> * The planet radius was updated in the abstract and throughout
>   the manuscript.

@@

******************************************
REFEREE COMMENT
----------
Sec. 4.3
The authors perform a joint fit of the TESS and ground-based
photometry to derive a more precise ephemeris, but fit only the
TESS data for the remaining planet parameters. If the errors on
the respective data sets are properly scaled (including jitter
terms if needed), the extra noise from the ground-based
photometry should not significantly impact the inferred
parameters when including those data. This is merely a comment,
and no extra work is necessary.

RESPONSE
----------
> Noted with thanks. As described above, we have amended our preferred
> solution to the TESS+ground solution, rather than the TESS-only
> solution.

@@

******************************************
REFEREE COMMENT
----------
Given the planet's young age, it would be interesting to know if
the transit photometry meaningfully constrains the eccentricity
(which along with impact parameter could explain the short
duration). Was a transit fit including eccentricity performed? If
not, there are methods to infer the eccentricity from the
posteriors of a circular orbit fit (see Dawson & Johnson 2012).

RESPONSE
----------
> While we agree that the possibility of a non-circular orbit would be
> interesting, we do not expect that given the present data we can
> make credible statements about potential non-zero eccentricities. We
> have updated the last paragraph of Sec 4.3 to justify this
> assumption of a circular orbit, and have amended the conclusion to
> mention this as a possible area for future work.

@@

******************************************
REFEREE COMMENT
----------
Discussion
More emphasis could be placed on the unusually large size of the
planet. Some speculative discussion on the nature of this
inflation could be warranted. Figure 11 might also be revised to
also reflect the effect of insolation (or the data plotted could
be restricted to close-in planets).

RESPONSE
----------
> Thank you for this suggestion. We have added a sub-plot in
> Figure 11 showing planet sizes and orbital periods, with the
> sub-100 Myr old planets emphasized.  We considered also
> including a plot with planet insolations on the ordinate
> instead of orbital periods, but the NASA Exoplanet Archive
> column for planet insolation is much less complete, presumably
> owing to the sparsity of available stellar luminosities.  We
> have also added some words in the discussion to the effect that
> that the young planets could be large because of i) a selection
> effect or ii) atmospheric escape.

******************************************
REFEREE COMMENT
----------
The paper ends on a note about nodal precession. Is it simple to
compute the nodal precession timescale given some reasonable
assumptions? This might help determine how likely it is that the
effect may be observed in the near term.

RESPONSE
----------
> Our thanks for this comment, which prompted us to calculate the
> precession frequency of the orbital axis due to the stellar
> oblateness using equations from Anderson+2018 and Lai+2018. We found
> that given the observed parameters of the system and an assumed
> stellar Love number (k2) equal to that of the Sun, the precession
> period would be 45,000 years. To complete say 1% of a precession
> cycle, which might roughly be what is needed to observe noticeable
> changes, we would need to wait ~450 years.
>
> We have correspondingly amended the last sentence to omit the point
> on nodal precession, in favor of the point that more photometry
> should improve our ability to constrain the orbital eccentricity,
> and will also let us search for additional transiting planets.

@@

******************************************
ADDITIONAL CHANGES

A few additional changes, most of which are noted in the "List of
Changes" appended at the end of the manuscript:

* Added citation to Bonomo+2017 in the introduction.

@@

* Citations to Donati+2020 and Damasso+2020 are added to clarify
  that the planetary nature of the RV-detected hot Jupiters in
  Taurus has been debated.

* Last paragraph of Sec 2.1: added transition sentence.

* Acknowledgements to K. Anderson, and to the referee, have been
  added.

* Table 5 has new rows for the ground-based transit nuisance
  parameters, and the posterior values are updated for the propagation
  of stellar parameter uncertainties.
